---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hpcalibrater

<!-- badges: start -->
<!-- badges: end -->

hpcalibrater creates a micro-calibrated ABM model for heat pump uptake by Irish households.

## Installation

You can install the development version of hpcalibrater like so:

``` r
# install_github()
```

## Example

Survey data for 804 owner-occupiers with 39 features plus HH ID and stated likelihood-to-adopt. 

```{r example, message=FALSE}
library(hpcalibrater)
library(tidyverse)
## basic example code
hp_survey_oo %>% dim()
```

Survey questions and answers are in:
```{r qanda,message=FALSE}
hp_questions %>% head()
```


Futher feature selection before passing to xgboost for model micro-calibration
```{r help}
## basic example code
feature_select(hp_survey_oo) %>% dim()
```

### Run GBM

The function `hpcalibrater::get_boosted_tree_model` generated a boosted tree object using XGBoost. SHAP scores are extracted from this object using `hpcalibrater::get_shap_scores`.

```{r bst, results='hide', message=FALSE}
bst <- get_boosted_tree_model(transform_to_utils(feature_select(hp_survey_oo,recode_bills=T,n_bill=5),epsilon=0.7))
shap_scores_long <- get_shap_scores(transform_to_utils(feature_select(hp_survey_oo,recode_bills=T,n_bill=5),epsilon=0.7),bst)

```

### Micro-calibrated ABM

Partial utilities from `shap_scores_long` based on financial feature (heating bills, **q13**), social feature (**q52**)

```{r mode_utils}
get_empirical_partial_utilities(shap_scores_long)
```

```{r model_weights}
weights <- get_model_weights(shap_scores_long,regularisation=1)
```
### Pairs plot
```{r pairs,message=F}
library(GGally)
weights[,-1] %>% ggpairs() + theme_minimal()
```
Note that there is a significant skew in the barrier weights ($\theta$)

